### 2014-12-19 ThesisJo/derivations.tex
la2pdf commit - 2014:12:10	12:08:06	(Wed10.Dec)
la2pdf commit - 2014:12:19	10:39:54	(Fri19.Dec)

Instead of solving the wave equation directly, we will make a qualified guess that the solution takes the form of a complex exponential in both time and space. For rectangular coordinates this can be written as:
%
\begin{align}
s(\p,t) &= A\,e^{j(\omega t - \k\cdot\p)}
\end{align}
%
Inserting this into the wave equation yields:
%
\begin{align}
\nabla^2 s = \frac{\partial^2 s}{\partial x^2} + \frac{\partial^2 s}{\partial y^2} + \frac{\partial^2 s}{\partial z^2} &= \frac{1}{c^2}\frac{\partial^2 s}{\partial t^2} \nn
(-jk_x)^2 s + (-jk_y)^2 s + (-jk_z)^2 s &= \frac{(-j\omega)^2}{c^2} s \nn
k_x^2 + k_y^2 + k_z^2 &= |\k|^2 = \frac{\omega^2}{c^2} \\
|\k| &= \frac{\omega}{c}
\end{align}
%
Hence, whenever we can assume the spatial and temporal frequency to be related directly by the sound speed, $|\k| = \frac{\omega}{c}$, then this assuming a complex exponential should be fair.

@@

\section{Roughness}

@@

\section{Beamforming}

>>>>

Instead of solving the wave equation directly, we will make a qualified guess that the solution takes the form of a complex exponential in both time and space. For rectangular coordinates this can be written as:
%
\begin{align}
s(\p,t) &= A\,e^{j(\omega t - \k\cdot\p)},
\end{align}
%
Inserting this into the wave equation yields:
%
\begin{align}
\nabla^2 s = \frac{\partial^2 s}{\partial x^2} + \frac{\partial^2 s}{\partial y^2} + \frac{\partial^2 s}{\partial z^2} &= \frac{1}{c^2}\frac{\partial^2 s}{\partial t^2} \nn
(-jk_x)^2 s + (-jk_y)^2 s + (-jk_z)^2 s &= \frac{(-j\omega)^2}{c^2} s \nn
k_x^2 + k_y^2 + k_z^2 &= |\k|^2 = \frac{\omega^2}{c^2} \\
|\k| &= \frac{\omega}{c}
\end{align}
%
This means that when we can assume the spatial and temporal frequency to be related directly by the sound speed, $|\k| = \frac{\omega}{c}$, then assuming a complex exponential to be a valid solution. Another solution of the wave equation is that of a spherical wave:
%
\begin{align}
s(r,t) &= \frac{A}{r}\,e^{j(\omega t - kr)}.
\end{align}

@@

\newpage
\section{Roughness}

@@

\newpage
\section{Beamforming}
